Paper 2: Vitamin D

### 2017-11-09 doc/vitaminD.Rmd
cleaned up gee output using functions

dsBase %>% 
  scatter_plot("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

@@

dsBase %>% 
  cor.test(formula = ~ VitaminD + udbpCr, data = ., method = "spearman")

@@

dsBase %>% 
  prep_mason_data() %>% 
  mason_glm(y = "VitaminD",
            x = "logudbpCr",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "fDM")
            ) %>% 
  dplyr::filter(!term == "(Intercept)") %>%
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

>>>>

dsBase %>% 
  scatter_plot("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D",
               "log UDBP:Creatinine")

@@

dsBase %>% 
  cor.test(formula = ~ log(udbpCr) + log(VitaminD), data = ., method = "spearman")

@@

dsBase %>% 
  dplyr::mutate(lVitD = log(VitaminD)) %>% 
  prep_mason_data() %>% 
  mason_glm(y = "logudbpCr",
            x = "lVitD",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "Season", "dmStatus")
            ) %>% 
  gee_results_table() %>% 
  pander::pander()
